---
editor_options:
  chunk_output_type: console
---

NOTES:

-   This file is *not* included in the [source package](https://r-pkgs.org/package-structure-state.html#source-package) because of the [`.nopurl` suffix in the
    filename](https://rpkg.dev/pkgpurl/reference/purl_rmd.html#-rmd-files-excluded-from-purling).

-   The chunks below have to be manually executed in order to regenerate the package data.

# Setup

```{r}
library(rlang,
        include.only = c("%|%", "%||%"))
library(magrittr,
        include.only = c("%>%", "%<>%", "%T>%", "%!>%", "%$%"))
```

# asciicasts

NOTES:

-   asciicasts are only regenerated manually because their generation takes a considerable amount of time. To regenerate an asciicast, manually run its code
    chunk, rebuild the package and finally re-build the vignette(s) where it's included.

-   After asciicasts are regenerated (and stored as JSON files under `inst/asciicasts/`), the package must be rebuilt in order to actually include the updated
    JSON files.

-   The asciicast player width of 116 chars (`cols = 116L`) is optimized for the current pkgdown layout of `rpkg.dev`.

## Verbose FOKUS questionnaire generation (Aargau \@ 2018-09-23)

```{r}
fs::dir_create("inst/asciicasts")
tmp_file <- fs::file_temp(ext = "R")

c('fokus:::gen_q_tibble(ballot_date = "2018-09-23",',
  '                     canton = "aargau",',
  '                     verbose = TRUE)') %>%
  readr::write_lines(file = tmp_file)

asciicast::record(script = tmp_file,
                  title = "Verbose FOKUS questionnaire generation (Aargau @ 2018-09-23)",
                  startup = quote(options(cli.width = 115L)),
                  timeout = 180L,
                  typing_speed = 0L,
                  rows = 50L,
                  cols = 116L,
                  speed = 0.75) %>%
  asciicast::write_json(path = "inst/asciicasts/gen_q_tibble-success.json")

fs::file_delete(tmp_file)
```

## Failed verbose FOKUS questionnaire generation (Aargau \@ 2018-09-23)

NOTES:

-   This code chunk generates a **failing** example. To trigger the error, an artificial mistake is temporarily added to the raw q
    (`the invalid inline code { 'intentional illustrative' 'error' }` at the beginning of item `first_name`'s `variable_label`).

```{r, eval = FALSE}
# temporarily add artificial mistake in raw q
yay::str_replace_file(path = "data-raw/questionnaire/questionnaire.toml",
                      pattern = c("(variable_label = \")(respondent's first name \\(official cantonal register information\\)\")" =
                                    "\\1{ 'intentional illustrative' 'error' }\\2"),
                      run_dry = FALSE,
                      verbose = FALSE)
fokus:::gen_pkg_data(data_files = "internal")
pkgload::unload()
devtools::install(quick = TRUE,
                  quiet = TRUE,
                  upgrade = "never")

# generate asciicast
tmp_file <- fs::file_temp(ext = "R")

c('fokus:::gen_q_tibble(ballot_date = "2018-09-23",',
  '                     canton = "aargau",',
  '                     verbose = TRUE)') %>%
  readr::write_lines(file = tmp_file)

asciicast::record(script = tmp_file,
                  title = "Failed verbose FOKUS questionnaire generation (Aargau @ 2018-09-23)",
                  startup = quote(options(cli.width = 115L)),
                  timeout = 180L,
                  typing_speed = 0L,
                  rows = 50L,
                  cols = 116L,
                  speed = 0.75) %>%
  asciicast::write_json(path = "inst/asciicasts/gen_q_tibble-failed.json")

fs::file_delete(tmp_file)

# restore raw q
yay::str_replace_file(path = "data-raw/questionnaire/questionnaire.toml",
                      pattern = c("(variable_label = \")\\{ 'intentional illustrative' 'error' \\}" =
                                    "\\1"),
                      run_dry = FALSE,
                      verbose = FALSE)

fokus:::gen_pkg_data(data_files = "internal")
pkgload::unload()
devtools::install(quick = TRUE,
                  quiet = TRUE,
                  upgrade = "never")
```
