---
editor_options:
  chunk_output_type: console
---

NOTES:

-   This file is *not* included in the [source package](https://r-pkgs.org/package-structure-state.html#source-package) because of the [`.nopurl` suffix in the
    filename](https://rpkg.dev/pkgpurl/reference/purl_rmd.html#-rmd-files-excluded-from-purling).

-   The chunks below have to be manually executed in order to regenerate the package data.

# Setup

```{r}
library(rlang,
        include.only = c("%|%", "%||%"))
library(magrittr,
        include.only = c("%>%", "%<>%", "%T>%", "%!>%", "%$%"))
```

# Exported data

NOTES:

-   When used internally, other than internal data, exported data must always be referred to by its explicit namespace, i.e. e.g. `fokus::qstnrs`.

## `qstnrs`

Questionnaire data as one single long-format tibble.

```{r}
qstnrs <-
  fokus::all_ballot_dates %>%
  magrittr::set_names(., .) %>%
  purrr::map(fokus::cantons) %>%
  purrr::imap(function(cantons, ballot_date) {
    
    cantons %>%
      purrr::map(~ fokus:::gen_qstnr_tibble(ballot_date = ballot_date,
                                            canton = .x) %>%
                   fokus:::validate_qstnr_tibble()) %>%
      purrr::list_rbind()
  }) %>%
  purrr::list_rbind() %>%
  # expand list cols
  tidyr::unnest(cols = any_of(fokus:::qstnr_item_keys_multival)) %>%
  # modify some vars
  dplyr::mutate(
    ## complete `question_full`
    question_full = question_full %|% question,
    ## merge `question_intro_i/j` into `question_intro`
    question_intro = paste(tidyr::replace_na(data = question_intro_i,
                                             replace = ""),
                           tidyr::replace_na(data = question_intro_j,
                                             replace = "")),
    ## complete `*_common` vars with their ballot-date/canton-specific siblings
    question_common = question_common %|% question_full,
    variable_label_common = variable_label_common %|% variable_label) %>%
  dplyr::select(-c(question_intro_i,
                   question_intro_j,
                   lvl,
                   i,
                   j)) %>%
  dplyr::relocate(question_intro,
                  .before = question) %>%
  # strip Markdown formatting from chr cols
  dplyr::mutate(dplyr::across(where(is.character),
                              pal::strip_md))
```

## `proposals`

```{r}
proposals <- 
  fokus::all_ballot_dates %>%
  purrr::map(function(ballot_date) {
    
    fokus::cantons(ballot_date) %>%
      purrr::map(ballot_date = ballot_date,
                 .f = function(canton,
                               ballot_date) {
                   
                   proposals_present <-
                     fokus::has_proposal_nrs(ballot_date = ballot_date,
                                             canton = canton) %>%
                     names() %>%
                     stringr::str_split(pattern = "\\.")
                   
                   tibble::tibble(ballot_date = ballot_date,
                                  lvl =
                                    proposals_present %>%
                                    purrr::map_depth(.depth = 1L,
                                                     .f = purrr::chuck,
                                                     1L) %>%
                                    purrr::list_c(ptype = character()),
                                  canton = canton,
                                  nr =
                                    proposals_present %>%
                                    purrr::map_depth(.depth = 1L,
                                                     .f = purrr::chuck,
                                                     2L) %>%
                                    as.integer(),
                                  type = purrr::map2_chr(lvl,
                                                         nr,
                                                         ~ fokus::proposal_type(ballot_date = !!ballot_date,
                                                                                lvl = .x,
                                                                                canton = !!canton,
                                                                                proposal_nr = .y)),
                                  name.de.short = purrr::map2_chr(lvl,
                                                                  nr,
                                                                  ~ fokus::proposal_name(ballot_date = !!ballot_date,
                                                                                         lvl = .x,
                                                                                         canton = !!canton,
                                                                                         proposal_nr = .y,
                                                                                         type = "short")),
                                  name.de.long = purrr::map2_chr(lvl,
                                                                 nr,
                                                                 ~ fokus::proposal_name(ballot_date = !!ballot_date,
                                                                                        lvl = .x,
                                                                                        canton = !!canton,
                                                                                        proposal_nr = .y,
                                                                                        type = "long")))
                 }) %>%
      purrr::list_rbind()
  }) %>%
  purrr::list_rbind()
```

## `elections`

```{r}
elections <- 
  fokus::all_ballot_dates %>%
  purrr::map(function(ballot_date) {
    
    fokus::cantons(ballot_date) %>%
      purrr::map(ballot_date = ballot_date,
                 .f = function(canton,
                               ballot_date) {
                   
                   elections_present <-
                     fokus::has_election_nrs(ballot_date = ballot_date,
                                             canton = canton) %>%
                     names() %>%
                     stringr::str_split(pattern = "\\.")
                   
                   tibble::tibble(ballot_date = ballot_date,
                                  lvl =
                                    elections_present %>%
                                    purrr::map_depth(.depth = 1L,
                                                     .f = purrr::chuck,
                                                     1L) %>%
                                    purrr::list_c(ptype = character()),
                                  canton = canton,
                                  prcd =
                                    elections_present %>%
                                    purrr::map_depth(.depth = 1L,
                                                     .f = purrr::chuck,
                                                     2L) %>%
                                    purrr::list_c(ptype = character()),
                                  nr =
                                    elections_present %>%
                                    purrr::map_depth(.depth = 1L,
                                                     .f = purrr::chuck,
                                                     3L) %>%
                                    as.integer(),
                                  name.de.short = purrr::pmap_chr(list(lvl,
                                                                       prcd,
                                                                       nr),
                                                                  ~ fokus::election_name(ballot_date = !!ballot_date,
                                                                                         lvl = ..1,
                                                                                         canton = !!canton,
                                                                                         prcd = ..2,
                                                                                         election_nr = ..3,
                                                                                         type = "short")),
                                  name.de.long = purrr::pmap_chr(list(lvl,
                                                                      prcd,
                                                                      nr),
                                                                 ~ fokus::election_name(ballot_date = !!ballot_date,
                                                                                        lvl = ..1,
                                                                                        canton = !!canton,
                                                                                        prcd = ..2,
                                                                                        election_nr = ..3,
                                                                                        type = "long")),
                                  name.de.body = purrr::pmap_chr(list(lvl,
                                                                      prcd,
                                                                      nr),
                                                                 ~ fokus::election_name(ballot_date = !!ballot_date,
                                                                                        lvl = ..1,
                                                                                        canton = !!canton,
                                                                                        prcd = ..2,
                                                                                        election_nr = ..3,
                                                                                        type = "body")))
                 }) %>%
      purrr::list_rbind()
  }) %>%
  purrr::list_rbind()
```

## Write data

Save all the bigger data objects to separate files under `data/*.rda`. Note that when documenting them, they mustn't be explicitly `@export`ed since they're
already automatically exported and thus available to package users.

```{r}
usethis::use_data(qstnrs,
                  proposals,
                  elections,
                  internal = FALSE,
                  overwrite = TRUE,
                  compress = "xz",
                  version = 3L)
```
