---
output: pal::gitlab_document
---

```{r}
#| label: init
#| include: false

knitr::opts_knit$set(root.dir = getwd())
```

# `r pal::desc_value("Package")`

`r paste0('[![CRAN Status](https://r-pkg.org/badges/version/', pal::desc_value(key = "Package"), ')](https://cran.r-project.org/package=', pal::desc_value(key = "Package"), '){.pkgdown-release}')`

`r pal::desc_value("Description")`

## Installation

```{r}
#| label: install-snippet-dev
#| child: !expr pkgsnip::snip_path("installation-notice_dev-version_gitlab.Rmd")
```

```{r}
#| label: usage
#| eval: !expr isTRUE(getOption("pal.build_readme.is_pkgdown"))
#| results: asis
#| echo: false

pkgsnip::md_snip(id = "usage_notice") %>%
  paste0("## Usage\n\n", .) %>%
  pal::cat_lines()
```

## Package configuration

```{r}
#| label: pkg-config
#| child: !expr pkgsnip::snip_path("pkg-config-notice.Rmd")
```

## Questionnaires

[![Netlify
Status](https://api.netlify.com/api/v1/badges/16855d14-c491-42cd-bc9d-a346e16b6672/deploy-status)](https://app.netlify.com/sites/qstnr-fokus-ag/deploys)

Generated survey questionnaires are automatically deployed to `qstnr.fokus.ag/{ballot_date}_{canton}.{ext}`, where `{ext}` is one of `html`, `md`, `csv` or
`xlsx`. The following questionnaires are available:

```{r}
#| label: qstnrs
#| echo: false
#| results: "asis"

fokus::all_ballot_dates |>
  purrr::map_chr(\(ballot_date) {
    fokus::cantons(ballot_date = ballot_date) |>
      purrr::map_chr(\(canton) {
        url_start <- glue::glue(fokus:::url_qstnr[[canton]], "/{ballot_date}_{canton}")
        glue::glue("-   {ballot_date} {stringr::str_to_title(canton)}: ",
                   "[{fontawesome::fa(name = 'fab fa-html5')}]({url_start}.html) | ",
                   "[{fontawesome::fa(name = 'fab fa-markdown')}]({url_start}.md) | ",
                   "[{fontawesome::fa(name = 'fas fa-file-csv')}]({url_start}.csv) | ",
                   "[{fontawesome::fa(name = 'fas fa-file-excel')}]({url_start}.xlsx)")
      }) |>
      paste0(collapse = "\n")
  }) |>
  paste0(collapse = "\n") |>
  cat()
```

## Private FOKUS directory structure

```{r}
#| label: fokus-private-desc
#| child: "data-raw/snippets/fokus_private_description.Rmd"
```

<details>

<summary><strong>Directory structure schema</strong></summary>

```{r}
#| label: fokus-private-schema
#| echo: false
#| results: "asis"

fokus:::print_private_repo_structure()
```

</details>

```{r}
#| label: documentation
#| eval: !expr '!isTRUE(getOption("pal.build_readme.is_pkgdown"))'
#| results: asis
#| echo: false

pkgsnip::md_snip(id = "pkgdown_notice") %>%
  paste0("## Documentation\n\n",
         "[![Netlify Status](https://api.netlify.com/api/v1/badges/0cc31095-153a-4d21-bec7-be8dd936ddf1/deploy-status)]",
         "(https://app.netlify.com/sites/fokus-rpkg-dev/deploys)\n\n",
         .) %>%
  pal::cat_lines()
```

## Development

### R Markdown format

```{r}
#| label: rmd-format
#| child: !expr pkgsnip::snip_path("rmd-package-notice.Rmd")
```

### Coding style

```{r}
#| label: coding-style
#| child: !expr pkgsnip::snip_path("coding-style-notice.Rmd")
```

### Abbreviations

The abbreviations used to name things (function and parameter names etc.) in this package include:

<details>

<summary><strong>Table of abbreviations</strong></summary>

```{r}
#| label: abbrs
#| echo: false

fokus:::abbrs() |>
  # flatten list col to comma-separted char col in order to avoid weird whitespacing before (some) commas (apparently `pal::pipe_table()` has flaws)
  dplyr::mutate(full_expressions = purrr::map_chr(full_expressions,
                                                  \(x) cli::ansi_collapse(x = x,
                                                                          sep2 = ", ",
                                                                          last = ", "))) |>
  dplyr::rename("Full expression(s)" = full_expressions,
                "Abbreviation" = abbreviation) |>
  pal::pipe_table()
```

</details>
