---
output: pal::gitlab_document
---

```{r}
#| label: init
#| include: false

knitr::opts_knit$set(root.dir = getwd())
```

# `r pal::desc_value("Package")`

`r paste0('[![CRAN Status](https://r-pkg.org/badges/version/', pal::desc_value(key = "Package"), ')](https://cran.r-project.org/package=', pal::desc_value(key = "Package"), '){.pkgdown-release}')`

`r pal::desc_value("Description")`

## Installation

```{r}
#| label: install-snippet-dev
#| child: !expr pkgsnip::snip_path("installation-notice_dev-version_gitlab.Rmd")
```

```{r}
#| label: usage
#| eval: !expr isTRUE(getOption("pal.build_readme.is_pkgdown"))
#| results: asis
#| echo: false
pkgsnip::md_snip(id = "usage_notice") %>%
  paste0("## Usage\n\n", .) %>%
  pal::cat_lines()
```

## Package configuration

```{r}
#| label: pkg-config
#| echo: false
#| results: "asis"

pkgsnip::md_snip(id = "pkg_config",
                 pkg = "fokus")
cat("\n\n::: {.table-wide}\n ")
pal::print_pkg_config("fokus")
cat("\n :::")
```

## Private FOKUS directory structure

```{r, child = "data-raw/snippets/fokus_private_description.Rmd"}
```

<details>

<summary><strong>Directory structure schema</strong></summary>

```{r, echo = FALSE, results = "asis"}
fokus:::print_fokus_private_structure()
```

</details>

```{r}
#| label: documentation
#| eval: !expr '!isTRUE(getOption("pal.build_readme.is_pkgdown"))'
#| results: asis
#| echo: false
pkgsnip::md_snip(id = "pkgdown_notice") %>%
  paste0("## Documentation\n\n",
         "[![Netlify Status](https://api.netlify.com/api/v1/badges/0cc31095-153a-4d21-bec7-be8dd936ddf1/deploy-status)]",
         "(https://app.netlify.com/sites/fokus-rpkg-dev/deploys)\n\n",
         .) %>%
  pal::cat_lines()
```

## Abbreviations

The abbreviations used to name things (function and parameter names etc.) in this package.

<details>

<summary><strong>Table of abbreviations</strong></summary>

```{r, echo = FALSE}
fokus:::abbrs() %>%
  # flatten list col to comma-separted char col in order to avoid weird whitespacing before (some) commas (apparently `pal::pipe_table()` has flaws)
  dplyr::mutate(full_expressions = purrr::map_chr(full_expressions,
                                                  pal::prose_ls,
                                                  last_sep = ", ")) %>%
  dplyr::rename("Full expression(s)" = full_expressions,
                "Abbreviation" = abbreviation) %>%
  pal::pipe_table()
```

</details>

## Development

### R Markdown format

```{r}
#| label: rmd-format
#| child: !expr pkgsnip::snip_path("rmd-package-notice.Rmd")
```

### Coding style

```{r}
#| label: coding-style
#| child: !expr pkgsnip::snip_path("coding-style-notice.Rmd")
```
