---
output: pal::gitlab_document
---

# `r paste0(pal::desc_value("Package"), ": ", pal::desc_value("Title"))`

`r pal::desc_value("Description")`

## Details

### R Options

The following package-specific R options are used to control the package's functionality:

```{r}
opts() %>%
  dplyr::mutate(name = paste0("`", name, "`"),
                "set automatically by `init()`" = lgl_to_unicode(is_auto_init)) %>%
  dplyr::select(-is_auto_init) %>%
  pal::pipe_table()
```

### Working directory structure

For part of this package's functionality the following structure of the working directory (defined by the R option `fokus.path_wd`) is expected (input) or enforced (output):

``` {.fs}
fokus_private/
├──bibliography/
|  ├──zotero_c2d.bib
|  └──zotero_c2d.json
├──config/
|  ├──csl/
|  ├──css/
|  ├──shared_pandoc_variables/`
|  |  ├──online_de.yaml
|  |  ├──online_en.yaml
|  |  ├──print_de.yaml
|  |  └──print_en.yaml
|  ├──config.toml
|  ├──output.yaml
|  ├──pandoc_template.tex
|  ├──shared_header-includes.tex
|  └──...
├──data/
|  └──[CANTON]/
|     ├──easyvote_municipalities_[BALLOT_DATE].csv
|     ├──online_participation_codes_[BALLOT_DATE].txt
|     ├──survey_data_[BALLOT_DATE].xlsx
|     ├──survey_data_[BALLOT_DATE]_*.xlsx
|     ├──survey_data_preliminary_[BALLOT_DATE].xlsx
|     ├──voting_register_data_extra_[STATOFF_DELIVERY_DATE].xlsx
|     ├──voting_register_ids_[BALLOT_DATE].csv
|     └──...
├──fonts/
|  └──...
├──images/
|  ├──[CANTON]/
|  |  └──[BALLOT_DATE]_*
|  └──...
├──questionnaires/
|  ├──print/
|  |  └──questionnaire_print_[BALLOT_DATE]_[CANTON].pdf
|  ├──proposals_[BALLOT_DATE].toml
|  ├──elections_[BALLOT_DATE].toml
|  └──questionnaire.toml
├──rmd/
|  ├──snippets/
|  |  ├──[CANTON]/
|  |  |  ├──[BALLOT_DATE]_cantonal_proposal_#.Rmd
|  |  |  ├──[BALLOT_DATE]_opinion_formation_and_participation.Rmd
|  |  |  ├──[BALLOT_DATE]_special_*.Rmd
|  |  |  ├──[BALLOT_DATE]_special_*_summary.Rmd
|  |  |  └──[BALLOT_DATE]_summary.Rmd
|  |  ├──imprint_de.Rmd
|  |  ├──imprint_en.Rmd
|  |  └──methodological_description.Rmd
|  ├──data_overview.Rmd
|  ├──questionnaire.Rmd
|  ├──paper_[BALLOT_DATE]_[CANTON].Rmd
|  ├──report_[BALLOT_DATE]_[CANTON].Rmd
|  ├──report_cantonal_majoritarian_[BALLOT_DATE]_[CANTON].Rmd
|  ├──report_cantonal_proportional_[BALLOT_DATE]_[CANTON].Rmd
|  ├──report_federal_majoritarian_[BALLOT_DATE]_[CANTON].Rmd
|  ├──report_federal_proportional_[BALLOT_DATE]_[CANTON].Rmd
|  └──special_*_[BALLOT_DATE]_[CANTON].Rmd
├──output/
|  ├──data/
|  |  ├──internal/
|  |  |  ├──r/
|  |  |  ├──spss/
|  |  |  └──stata/
|  |  ├──public/
|  |  └──publitest/
|  ├──images/
|  |  ├──[BALLOT_DATE]/
|  |  |  └──[CANTON]/
|  |  |     └──...
|  |  └──qr_codes/
|  |     └──[BALLOT_DATE]_[CANTON].zip
|  ├──questionnaires/
|  |  ├──questionnaire_[BALLOT_DATE]_[CANTON].csv
|  |  ├──questionnaire_[BALLOT_DATE]_[CANTON].html
|  |  ├──questionnaire_[BALLOT_DATE]_[CANTON].md
|  |  └──questionnaire_[BALLOT_DATE]_[CANTON].xlsx
|  ├──publications/
|  |  ├──libs/
|  |  └──...
|  └──rmd/
|     └──[BALLOT_DATE]/
|        └──[CANTON]/
|           └──plots/
├──tools/
|  └──pandoc/
|     ├──linux/
|     ├──macos/
|     └──windows/
├──README.Rmd
└──...
```

The following placeholders are used in the schema above:

-   `...` for further files and/or folders
-   `*` for a variable character sequence
-   `#` for a count starting with `1`
-   `[CANTON]` for the name of the current canton given by the R option `fokus.canton` (in lower case)
-   `[BALLOT_DATE]` for the current ballot date given by the R option `fokus.date_ballot` (in the format `YYYY-MM-DD`)
-   `[STATOFF_DELIVERY_DATE]` for the delivery date of the voting register data provided by the cantonal statistical office

## Installation

```{r, install-snippet-dev, child = pkgsnip::snip_path("installation-notice_dev-version_gitlab.Rmd")}
```

## Development

### R Markdown format

```{r, rmd-pkg-snippet, child = pkgsnip::snip_path("rmd-package-notice.Rmd")}
```

### Coding style

```{r, coding-style-snippet, child = pkgsnip::snip_path("coding-style-notice.Rmd")}
```

------------------------------------------------------------------------

