---
output: pal::gitlab_document
---

# `r paste0(pal::desc_value("Package"), ": ", pal::desc_value("Title"))`

`r pal::desc_value("Description")`

## Details

### R Options

The following package-specific R options are used to control the package's functionality:

```{r, echo = FALSE}
fokus:::print_opts()
```

### Working directory structure

For part of this package's functionality, the following structure of the working directory (defined by the R option `fokus.path_wd`) is expected (input) or
enforced (output):

```{r, echo = FALSE, results = "asis"}
fokus::print_wd_structure()
```

```{r, pkgdown, eval = !isTRUE(getOption("pal.build_readme.is_pkgdown")), results = "asis", echo = FALSE}
pkgsnip::md_snip(name = "pkgdown_notice") %>%
  paste0("## Documentation\n\n", .) %>%
  pal::cat_lines()
```

## Installation

```{r, install-snippet-dev, child = pkgsnip::snip_path("installation-notice_dev-version_gitlab.Rmd")}
```

## Development

### R Markdown format

```{r, rmd-pkg-snippet, child = pkgsnip::snip_path("rmd-package-notice.Rmd")}
```

### Coding style

```{r, coding-style-snippet, child = pkgsnip::snip_path("coding-style-notice.Rmd")}
```
