---
title: "FOKUS questionnaire schema"
subtitle: "Structure and semantic rules of the raw TOML questionnaire"
date: "`r if (git2r::in_repository()) as.Date(pal::git_file_mod_time('vignettes/raw_qstnr_schema.Rmd')) else Sys.Date()`"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 6
editor_options:
  chunk_output_type: console
vignette: >
  %\VignetteIndexEntry{FOKUS questionnaire schema}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r}
#| label: setup
#| include: false

# set RNG seeds
set.seed(42L)
htmlwidgets::setWidgetIdSeed(seed = 42L)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Main semantic rules

The [raw questionnaire](https://gitlab.com/zdaarau/rpkgs/fokus/-/tree/master/data-raw/questionnaire/questionnaire.toml) is written in the [TOML file
format](https://toml.io/en/latest). Basically, all questionnaire items are defined in an [ordered tree
structure](https://en.wikipedia.org/wiki/Tree_(graph_theory)#Ordered_tree) where child nodes inherit the attributes of their parent (and transitively
grandparent etc.) nodes.

The following main semantic rules apply:

1.  Top table level (`blockname`) defines a questionnaire block[^1], whereby the (alphabetical) order of the table levels conforms to the order of the blocks in
    the questionnaire:

    ``` toml
    [blockname]
    ```

2.  Lower table level names ideally start with a 3-digit number (`###`) since table levels (and hence questionnare items below them) are always ordered
    according to the (alphabetical) order of their names:

    ``` toml
    [blockname.00X_2nd_lvl.00X_3rd_lvl]
    ```

3.  Deepest[^2] table level named `item` defines an "atomic" questionnaire item (= single row in Markdown questionnaires) or a template for multiple similar
    "atomic" questionnaire items. It can be defined multiple times (once for each item) and must be wrapped in double brackets:

    ``` toml
    [[blockname.00X_2nd_lvl.00X_3rd_lvl.item]]
    ```

    Items appear in the final questionnaire in the same order they are defined here. Technically, the level `item` is an [array of
    tables](https://toml.io/en/latest#array-of-tables) which is represented as a list of unnamed lists in R.

4.  Table levels in between top and deepest level `item` can be named anything except `variable_name` and are intended to arrange and/or group items and set
    keys that hold for multiple questionnaire items hierarchically in order to avoid redundancies.

    **NOTE:** It is still strongly discouraged to name table levels the same as any of the keys listed below.

[^1]: Exceptions: The following tables/table arrays are not questionnaire blocks by themselves, but also don't contain "atomic" questionnaire items.

    -   `title`
    -   `who`
    -   `party`
    -   `response_options`
    -   `footnote`
    -   `link`

[^2]: The term "deepest" is kind of misleading here since there can actually be TOML table levels below the level of an "atomic" questionnaire item, namely to
    define `include` rules (e.g. `include.false = [ YYYY-MM-DD ]`) or to account for varying `topic`, `question` etc. wordings at different ballot dates (e.g.
    `topic.default = "bla"` and `topic.YYYYMMDD = "blup"`) or for different ballot types (e.g. `topic.default.election = "bla"` and
    `topic.default.referendum = "blup"`).

# Supported keys

Depending on the table level, the set of possible keys includes:

-   Only regarded on top level ("block"):

    | Key      | Type             | Optional | Remarks                                                                                                                                          |
    |----------|------------------|----------|--------------------------------------------------------------------------------------------------------------------------------------------------|
    | `title`  | character scalar | ❌       | block title                                                                                                                                      |
    | `intro`  | character scalar | ✅       | text paragraph introducing the questionnaire items of the block                                                                                  |
    | `prefix` | integer scalar   | ✅       | block numbering prefix for the first questionnaire column `#`; if not provided, items will be auto-numbered across all blocks without a `prefix` |

-   Regarded on all levels incl. individual `item`-level nodes:

```{r}
#| echo: false
#| results: "asis"

library(magrittr)
options(knitr.kable.NA = '')

fokus:::qstnr_item_keys %>%
  dplyr::select(key, type, default, is_optional, everything()) %>%
  dplyr::mutate(key = pal::wrap_chr(key,
                                    wrap = "`"),
                type = paste(type, dplyr::if_else(is_scalar,
                                                  "scalar",
                                                  "vector")),
                default = pal::wrap_chr(default,
                                        wrap = "`"),
                dplyr::across(where(is.logical),
                              fokus:::lgl_to_unicode)) %>%
  dplyr::select(-c(is_scalar,
                   default_val)) %>%
  dplyr::rename("Default value" = default) %>%
  dplyr::rename_with(.cols = starts_with("is_"),
                     .fn = stringr::str_remove,
                     pattern = "^is_") %>%
  dplyr::rename_with(stringr::str_to_title) %>%
  pal::pipe_table() %>%
  paste0("    ", .) %>%
  pal::cat_lines()
```

The keys regarded on `item`-level nodes are resolved in the following order

1.  `lvl`
2.  `i`
3.  `j`
4.  All the other item-level keys[^3].

[^3]: Except for `question` which can be referenced by `question_full` via string interpolation and hence is resolved before the latter.

# Further notes

-   All keys support [glue's string interpolation](https://glue.tidyverse.org/), meaning that non-character-type keys like `include` or `variable_values` can
    also be specified as string (arrays) which will automatically be converted to their proper type during questionnaire generation.

    More specifically, keys that hold *arrays* like `response_options` are fed to [`glue::glue()`](https://glue.tidyverse.org/reference/glue.html) allowing to
    use its powerful [string interpolation syntax](https://glue.tidyverse.org/), while the other keys holding *scalars* like `include` are fed to
    [`cli::pluralize()`](https://cli.r-lib.org/reference/pluralize.html) which additionally supports a [handy pluralization
    syntax](https://cli.r-lib.org/articles/pluralization.html). The default behavior of trimming all surrounding whitespaces is disabled in both cases.

-   To vary *non-binary keys* like `topic`, `question` etc. wordings for different cantons and/or ballot dates directly without relying on embedded R code, you
    can define

    -   single-canton subkeys named by the lowercase English canton name (e.g. `aargau`) applying to a specific canton,
    -   single-date subkeys named `YYYYMMDD` (the respective ballot date without any `-`) applying to a specific ballot date,
    -   begin-end interval subkeys named `YYYYMMDD_YYYYMMDD` applying to all ballot dates that fall into the specified interval, or
    -   `default` applying to any canton or ballot date for which no more specific subkey exists.

    Interval subkeys mustn't overlap. Single-date subkeys have precedence over interval subkeys and canton subkeys have precedence over any date subkeys.

    To vary *binary keys* like `allow_multiple_answers` or `include` directly, you can define

    -   begin-end interval subkeys as described above, or alternatively
    -   subkeys named `true` (meaning inclusion) or `false` (meaning exclusion; has priority over `true` in case of ambiguity) containing an array of cantons or
        dates (`YYYY-MM-DD`), as well as
    -   `default` (applying to any cantons or ballot dates not included in the `true` or `false` subkeys).

    The `true`/`false` subkeys have precedence over begin-end interval subkeys. Subkey can be combined by nesting them.

    To vary keys for different ballot types, just define subkeys named `referendum` or `election`.

    Examples:

    ```         
    topic.default = "bla"
    topic.aargau = "oops"
    topic.zurich = "upsala"
    who.20180923 = "alle"
    who.20181125_20201018 = "Online-Respondenten"
    who.20181125_20201018.zurich = "Print-Respondenten"
    include.default = true
    include.false = [ 2018-09-23 ]
    question.default.election = "lalala"
    question.default.referendum = "nenene"
    ```

    **NOTES:**

    -   `variable_name` is the only key that mustn't have any subkeys.
    -   If `variable_label_common` is not explicitly defined, it falls back to `variable_label.default`.
    -   If `question_common` is not explicitly defined, it falls back to a) the `question_full.default`, b) `question.default`, or c) `question_full`.

-   The keys `lvl`, `i` and `j` are interpreted as iterators which you can refer to via string interpolation (e.g. `voting_decision_{lvl}`), so you have to
    define similar questionnaire items only once. If any of them evaluate to `NULL` or an empty vector, the respective item is automatically excluded, i.e. it's
    not necessary to explicitly set `include` (sub)keys in such case.

-   You can even cross-reference keys from non-parent nodes using [`qstnr_item_val()`](https://fokus.rpkg.dev/reference/qstnr_item_val.html). But be careful to
    not create infinite loops via circular references.

-   To explicitly unset a key, just assign a string containing `NA` of the correct type wrapped in curly braces (`"{NA_character_}"` for values of type string,
    `"{NA_integer_}"` for values of type integer etc.).

-   A `who` constraint notice is automatically added to the end of `variable_label` and `variable_label_common` if possible (e.g. `"blabla (only non-voters)"`).
    Because `variable_label_common` by definition mustn't vary over time, it **must** be explicitly specified *including such a `who` constraint notice* **if**
    `who` varies over time.

-   This questionnaire is [complemented by a **supplemental TOML file `YYYY-MM-DD.toml`** for each ballot
    date](https://gitlab.com/zdaarau/rpkgs/fokus/-/tree/master/data-raw/questionnaire/) that holds additional date-specific metadata.

# Supplemental assumptions to resolve glue/cli string interpolation

-   The following R packages are loaded and [attached](https://rdrr.io/r/base/library.html).

    -   [fokus](https://fokus.rpkg.dev/)
    -   [magrittr](https://magrittr.tidyverse.org/)

-   The following R objects are present in the evaluation environment:

    -   `ballot_date` (character scalar): The ballot date the questionnaire is to be generated for (in the format `YYYY-MM-DD`).

    -   `canton` (character scalar): The canton the questionnaire is to be generated for (all lowercase).

# Debugging

The R function [`fokus:::gen_qstnr_tibble()`](https://fokus.rpkg.dev/reference/gen_qstnr_tibble.html), which is designed to turn the raw questionnaire into a
[tibble](https://tibble.tidyverse.org/reference/tbl_df-class.html) containing the questionnaire data for a specific ballot date and canton, prints helpful
progress information when its `verbose` argument is set to `TRUE` (default is `FALSE`).

For the questionnaire \@ 2018-09-23 in Aargau, this looks as follows:

```{r}
#| echo: false

fs::path_package("asciicasts/gen_qstnr_tibble-success.json",
                 package = "fokus") %>%
  asciicast::read_cast() %>%
  # playback speed is not stored in the asciicast itself, so has to be set here
  asciicast::asciinema_player(speed = 1)
```

If some mistake that breaks questionnaire generation is present in the raw questionnaire, like a syntax error in embedded R code for example, the progress
output stops immediately, allowing to easily locate the exact source position of the mistake.
